Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML

### 2014-02-17 paper.tex
Fixed typo.

Whilst there are successful general web search engines such a Google that
will find any piece of content, there is a perceived need for a specific
search that makes better use of the internal knowledge the broadcasting
industry (e.g. BBC) has about its own content. The British Broadcasting
Corporation (BBC) is a public service broadcaster funded by the licence
fee paid by United Kingdom households. This industry-based case study
combines Soft Systems Methodology (SSM) and Unified Modelling Language
(UML) to design a high-level view of a search application that receives
web content from a variety of BBC content production systems and makes
every item then searchable by a BBC website visitor using the search
feature. The developers of such search applications can benefit from this
specific industry-based case study that contextualised the problem space
using SSM and developed UML models to solve the problem.

>>>>

Whilst there are successful general web search engines such as Google that
will find any piece of content, there is a perceived need for a specific
search that makes better use of the internal knowledge the broadcasting
industry (e.g. BBC) has about its own content. The British Broadcasting
Corporation (BBC) is a public service broadcaster funded by the licence
fee paid by United Kingdom households. This industry-based case study
combines Soft Systems Methodology (SSM) and Unified Modelling Language
(UML) to design a high-level view of a search application that receives
web content from a variety of BBC content production systems and makes
every item then searchable by a BBC website visitor using the search
feature. The developers of such search applications can benefit from this
specific industry-based case study that contextualised the problem space
using SSM and developed UML models to solve the problem.
